Rapid cycleway prioritisation tool

### 2020-06-05 code/index.Rmd
Update text, typo fixes for r

Reallocating road space on strategic corridors is just one of the measures available for transport authorities.
Evidence provided by the tool can also support a range of temporary, experimental and permanent treatments that will enable rapid and safe uptake of cycling.
New [statutory guidance on network management in response to COVID-19](https://www.gov.uk/government/publications/reallocating-road-space-in-response-to-covid-19-statutory-guidance-for-local-authorities/traffic-management-act-2004-network-management-in-response-to-covid-19) outlines a range of measures, including the creation of new cycleways, reducing speed limits, widening of footways and closing roads to motor traffic via 'modal filters'.
Road space reallocation is suited to larger roads and can have a large impact quickly, especially when moving large numbers of people away from public transport and capacity is a priority.
Furthermore, low but gradually increasing levels of peak hour motor traffic mean that there is a window of opportunity to reallocate lanes without causing congestion in the short term.

@@

The cycling potential of each road is based on the Government Target (equality) scenario from the Propensity to Cycle Tool. 
The numbers represents the number of one way cycle trips to work and school that could be expected when the [Government's aim of doubling cycling is met](https://www.gov.uk/government/publications/cycling-and-walking-investment-strategy).
Our figures include data on travel to work from 2011 Census data and travel to school, assuming cycling grows evenly nationwide accounting for distance and hilliness [@lovelace_propensity_2017; @goodman_scenarios_2019]
Data on road widths and number of lanes is derived from the Cycling Infrastructure Prioritisation Toolkit (see [cyipt.bike](https://www.cyipt.bike/)).

@@

On the basis that plans should build on and extend existing provision, this layer shows existing cycleways.
This may be helpful to view in connection with the other layers, because it can reveal where gaps in the existing cycle network could be filled by new infrastructure.
<!-- This layer does not include some on-road cycle lanes or cycleways less than 500m in length, but these can be viewed in one of the basemap options (see below for more information about the basemaps). -->
The definition of 'cycleway' includes shared use paths but excludes cycle lanes painted on roads in this layer.

@@

These are the 'top n' road sections in terms of cycling potential with 'spare space' defined above.
They may be suitable candidates for road space reallocation to create new cycleways. 
These roads have either a spare lane or an average width greater than 10 m, and are ranked according to their mean cycling potential. 
<!-- For routes that are shorter than 1km in length, we use 'km_cycled' instead of mean cycling potential - this is simply the mean cycling potential multiplied by the length of the route.  -->
Top ranked new cycleways are listed in the table below the map, so you can see more information on them. 
The number of Top ranked new cycleways varies depending on the size of the region.

>>>>

Reallocating road space on strategic corridors is just one of the measures available for transport authorities.
Evidence provided by the tool can also support a range of temporary, experimental and permanent treatments that will enable rapid and safe uptake of cycling.
New [statutory guidance on network management in response to COVID-19](https://www.gov.uk/government/publications/reallocating-road-space-in-response-to-covid-19-statutory-guidance-for-local-authorities/traffic-management-act-2004-network-management-in-response-to-covid-19) outlines a range of measures, including the creation of new cycleways, reducing speed limits, widening of footways and closing roads to motor traffic via 'modal filters'.
Road space reallocation is suited to larger roads and can have a large impact quickly, especially where moving large numbers of people away from public transport and capacity is a priority.
Furthermore, low but gradually increasing levels of peak hour motor traffic mean that there is a window of opportunity to reallocate lanes without causing congestion in the short term.

@@

The cycling potential of each road is based on the Government Target (equality) scenario from the Propensity to Cycle Tool. 
The figures given represent the numbers of one way cycle trips to work and school that could be expected on each road, in a scenario where the [ Government’s aim of an overall doubling of cycling trips has been met](https://www.gov.uk/government/publications/cycling-and-walking-investment-strategy).
Our figures include data on travel to work from 2011 Census data and travel to school, assuming cycling grows evenly nationwide accounting for distance and hilliness [@lovelace_propensity_2017; @goodman_scenarios_2019]
Data on road widths and number of lanes is derived from the Cycling Infrastructure Prioritisation Toolkit (see [cyipt.bike](https://www.cyipt.bike/)).

@@

On the basis that plans should build on and extend existing provision, this layer shows existing cycleways.
This may be helpful to view in connection with the other layers, because it can reveal where gaps in the existing cycle network could be filled by new infrastructure.
<!-- This layer does not include some on-road cycle lanes or cycleways less than 500m in length, but these can be viewed in one of the basemap options (see below for more information about the basemaps). -->
The definition of ‘cycleway’ for the purpose of this layer includes shared use paths but excludes cycle lanes painted on roads.

@@

These are the 'top n' road sections in terms of cycling potential with 'spare space' as defined above.
They may be suitable candidates for road space reallocation to create new cycleways. 
These roads have either a spare lane or an average width greater than 10 m, and are ranked according to their mean cycling potential. 
<!-- For routes that are shorter than 1km in length, we use 'km_cycled' instead of mean cycling potential - this is simply the mean cycling potential multiplied by the length of the route.  -->
Top ranked new cycleways are listed in the table below the map, so you can see more information on them. 
The number of Top ranked new cycleways varies depending on the size of the region.
